SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-10-25 docs/questioning.tex
exploitation model text ready

Then, the injected code reaches the vulnerable
application where it probably becomes a part of a value
represented by a program variable.
In the next step, the code becomes a part of a query which
finally reaches the database where it is executed.
Attacks like {\sc sql} injection and {\sc csrf}
end right there.

Before we proceed with the {\sc xss} attack path,
we should mention here that there are two basic
{\sc xss} attack categories, namely:
{\it non-persistent} and {\it persistent}.
Non-persistent {\sc xss} attacks take place when the data provided
by a user, is used immediately by server-side scripts to parse
and display a page of results for and to that user, without
properly sanitizing the request. In the case of a
persistent {\sc xss} attack, malicious code
is saved by the server, and then permanently
displayed on the web site's pages that are displayed
to other users.

% A {\sc persistent} {\sc xss} attack though would
% continue
% An {\sc xss} attack that belongs to the {\it non-persistent}
% {\sc xss} category could have followed a different path.
% This is because

@@

>>>>

Then, the injected code reaches the vulnerable
application where it becomes a part of a value
represented by a program variable.
In the next step, the code becomes a part of a query that
finally reaches the database where it is executed.
Attacks like {\sc sql} injection and {\sc csrf}
end right there.

Before we proceed with the {\sc xss} attack path,
we should mention that there are two basic
{\sc xss} attack categories, namely:
{\it non-persistent} and {\it persistent}.
Non-persistent {\sc xss} attacks take place when the data provided
by a user, is used immediately by server-side scripts to parse
and display a page of results for and to that user, without
properly sanitizing the request. In the case of a
persistent {\sc xss} attack, malicious code
is saved by the server, and then permanently
displayed on the web site's pages that are displayed
to other users. Thus, in a non-persistent {\sc xss}
attack the injected code never reaches the database
and immediately becomes a part of the content that is
sent back to a web user. In the case of a persistent
{\sc xss}, the injected code that is stored on the server-side
re-enters the application's execution flow and afterwards it
becomes a part of the content that is actually sent back to
the user.

@@

\section{Conclusions}

% Cite~\cite{HNSHS12}.
